\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

All test-cases were performed in an idealised geometry discretised with unstructured triangular \PN[1]{2} and \PN[1]{1} FE mesh. In most simulations, the domain was initially fully saturated with the non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity ($u$). For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$

>>>>

All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. The set-up for the numerical simulations are summarised in Table \ref{table:setup}.

### 2017-05-10 Papers/ViscousInstabilities/article_table.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & MR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
    \hline
      \ref{section:results:validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
      \ref{section:results:heleshaw}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
                                       & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
      \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $0$ denotes initial condition. \red{(KOSTAS, PLEASE: DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES AND REPLACE ALL XX; $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}
\end{table}

>>>>

\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
    \hline
      \ref{section:results:validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
      \ref{section:results:heleshaw}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
                                       & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
      \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $0$ denotes initial condition. \red{(KOSTAS, PLEASE: 1. DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2. REPLACE ALL XX; 3. COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}\label{table:setup}
\end{table}
